On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-09-29 paper/paper.tex
Add a couple of TODOs and go into more detail in the first example in the paper

@@

In the example below, the Core plugin transforms \ttt{example} into \ttt{example'}:
\begin{lstlisting}[deletekeywords={Ord}]
import Data.Char (ord)

@@

example :: Int
example =
  internalize (externalize
    (case x of
      Left  c -> ord c
      Right i -> i))

example' :: Int
example' =
  abs (CaseExp
        (LeftExp 'a')
        (SumMatchExp (OneProdMatch
                       (Lam 1
                         (Ord (Var 1))))
                     (OneSumMatch
                       (OneProdMatch
                         (Lam 2
                           (Var 2)))))
\end{lstlisting}

@@

% \begin{todo}
%   Figure out how recursive types fit into this framework. Church encodings can
%   handle recursive types and so can our representation. This is also the case
%   for Scott encodings, etc, and is the difference between Church and Scott
%   encodings.

%   Does our way of handling recursive types correspond to how any of
%   those encodings handle recursive types?

%   Maybe this is relevant: \href{https://www.reddit.com/r/haskell/comments/hvlh6a/generalized_church_encoding_is_the_curryhoward_of/}{\color{blue}{Generalized Church encoding is the Curry-Howard of Knaster-Tarski}}
% \end{todo}

>>>>

\begin{todo}
  Make it more clear how to integrate these concepts with other EDSLs. Maybe we should
  add a feature to the underlying implementation that allows an existing EDSL to be
  "enriched" with pattern matching support.
\end{todo}

@@

In the example below, the Core plugin transforms \verb|example| into
\verb|example'|. Note that \verb|example'| is an EDSL expression which is then
used by the EDSL interpreter function \verb|abs| to produce the final result,
\verb|example''|:

\begin{lstlisting}[deletekeywords={Ord}]
import Data.Char (ord)

@@

example :: Int
example =
  externalize
    (case x of
      Left  c -> ord c
      Right i -> i)

example' :: E Int
example' =
  CaseExp
        (LeftExp 'a')
        (SumMatchExp (OneProdMatch
                       (Lam 1
                         (Ord (Var 1))))
                     (OneSumMatch
                       (OneProdMatch
                         (Lam 2
                           (Var 2)))))

example'' :: Int
example'' = abs example'
\end{lstlisting}

@@

\begin{todo}
  Figure out how recursive types fit into this framework. Church encodings can
  handle recursive types and so can our representation. This is also the case
  for Scott encodings, etc, and is the difference between Church and Scott
  encodings.

  Does our way of handling recursive types correspond to how any of
  those encodings handle recursive types?

  Maybe this is relevant: \href{https://www.reddit.com/r/haskell/comments/hvlh6a/generalized_church_encoding_is_the_curryhoward_of/}{\color{blue}{Generalized Church encoding is the Curry-Howard of Knaster-Tarski}}
\end{todo}
